A formal approach but practical approach in train regulation

### 2025-06-24 paper/main.tex
Modification des états pour ajouter le buffer de signaux

%% Buffer
\newcommand{\bufferFmt}[1]{#1}
\newcommand{\head}[1]{\ensuremath{{\tt hd}(#1)}}
\newcommand{\buflen}[1]{\ensuremath{{\tt len}(\bufferFmt{#1})}}
\newcommand{\bufhead}[1]{\head{\bufferFmt{#1}}}
\newcommand{\buftail}[1]{\ensuremath{{\tt tl}(\bufferFmt{#1})}}
\newcommand{\emptyList}{\ensuremath{\varepsilon}}
\newcommand{\bufferSet}{\ensuremath{\bufferFmt{\mathbb{B}}}\xspace}

%% Reduction relation
\newcommand{\reduces}{\ensuremath{\rightarrow}}
\newcommand{\redTuple}[3]{\ensuremath{\tuple{#1, #2, #3}}}

@@

Train events are not dealt with instantly by the regulator (e.g. two train events can happen before the regulator begins to react to the first one). To characterise this behaviour, train events are stored in a buffer until the regulator uses them. Train events are tuples \tuple{\tid{id}, \bid{id}}, indicating that the train with id $\tid{id}$ enters block \bid{id}. A buffer \bufferFmt{B} is a sequence of such events. Let \bufferSet{} be the set of all buffers.

Similarly, the regulator communicates with signals with a \emph{signal buffer} $B_s$, which is a list of tuple $\tuple{\bid{id}, c}$, indicating that both signals of block $\bid{id}$ should be turned to color $c$. \todo{mise en page}

@@

States of the system are triples from $\{\guardR, \guardS, \guardT\} \times \bufferSet \times \modelSet$. Our reduction relation is a binary relation on system states, noted $\reduces$: $S_1 \reduces S_2$ means that state $S_1$ can change to $S_2$ (note that this relation is not a function: $S_1$ can reduce to multiple states, due to non-determinism). We define $\reduces$ as the least relation induced by the inference rules presented hereafter.

@@

\todo{Enlever les bid dans le buffer des trains}
\begin{mathpar}
	\inferrule*[left=\ruleDef{Start}]{
		\dirFmt{d} \neq \dirFmt{d^\prime} \and P = \trainConcat{\su{d^\prime}{\posFmt{N}}}{P^\prime}
	}{
		\hspace{3mm} \redTuple{\guardT}{\bufferFmt{B}}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{P}\}}{\regulator}{\switches}{\signals}} \\
		\reduces
		\redTuple{\guardT}{\push{B}{\tuple{\tid{id}, \bid{id}}}}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d^\prime}{P}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}

Conversely, if the train program is empty (i.e. upon termination), the train stops using rule \ruleRef{Stop}.
\begin{mathpar}
	\inferrule*[left=\ruleDef{Stop}]{
		\dirFmt{d} \neq \dirStop
	}{
	\hspace{4mm}  \redTuple{\guardT}{\bufferFmt{B}}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\emptyTrainProg}\}}{\regulator}{\switches}{\signals}} \\
	\reduces
	\redTuple{\guardT}{\push{B}{\tuple{\tid{id}, \bid{id}}}}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{\dirStop}{\emptyTrainProg}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{Until}] {
		\suc{\bid{id}}{d}{\switches} = \bid{id^\prime} \neq \nosuc
		\and
		\signalF{\bid{id}}{d} = \siggreen
		\and
		\posFmt{N}\neq \varepsilon
	}{
		\redTuple{\guardT}{\bufferFmt{B}}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\trainConcat{\su{d}{[\bid{id^\prime}; \posFmt{N}]}}{P}}\}}{\regulator}{\switches}{\signals}} \\
		\reduces		
		\redTuple{\guardS}{\push{\bufferFmt{B}}{\tuple{\tid{id}, \bid{id^\prime}}}}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id^\prime}}{d}{\trainConcat{\su{d}{[\posFmt{N}]}}{P}}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}

\begin{mathpar}
	\inferrule*[left=\ruleDef{UntilNext}] {
		\suc{\bid{id}}{d}{\switches} = \bid{id^\prime} \neq \nosuc
		\and
		\signalF{\bid{id}}{d} = \siggreen
	}{
		\redTuple{\guardT}{\bufferFmt{B}}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\trainConcat{\su{d}{[\bid{id^\prime}]}}{P}}\}}{\regulator}{\switches}{\signals}} \\
		\reduces		
		\redTuple{\guardS}{\bufferFmt{B}}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id^\prime}}{d}{P}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}
Notice that, in \ruleRef{UntilNext}, no message is added to the buffer.
\todo{@Lucas, expliquer pourquoi c'est pas nécessaire.}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{StartEvent}] {
		\buflen{B} \neq 0
	}{
		\tuple{\guardT, B, R} \reduces \tuple{\guardR, B, R}
	}
\end{mathpar}

@@

Rule \ruleRef{Turn} triggers when a \turn{\sid{id}}{s} is encountered in the event handler. It updates the state of the targeted switch.
\begin{mathpar}
	\inferrule*[left=\ruleDef{Turn}]{
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\turn{\sid{id}}{s}}{A^\prime}
	}{
	\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
	\reduces
	\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T, W}}{\updateSignals{\switches}{\sid{id}}{s}}{\signals}}
	}
\end{mathpar}

@@

To execute a \wait{\bid{critical}}{n} order, the regulator stores the train id in its waiting set, together with the current block of the train (\bid{src}), the block it is waiting for (\bid{critical}), and the value the token associated with the target block has to reach to release the train ($n$).
\begin{mathpar}
	\inferrule*[left=\ruleDef{WaitBefore}] {
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\wait{\bid{critical}}{n}}{A^\prime}
		\\
		\tokenOf{\bid{critical}} \neq n
	}{
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\reduces
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T, W\cup\tuple{\bid{src}, \bid{critical}, n, \tid{id}}}}{\switches}{\signals}}
	}
\end{mathpar}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{IncrAfter}] {
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\incr{\bid{critical}}}{A^\prime}
		\\
		\exists \bid{src}, \tid{waiting} \text{ s.t. } \tuple{\bid{src}, \bid{critical}, \tokenOf{\bid{critical}} + 1, \tid{waiting}} \in W
		\\
		\nextWait{\handlerOf{E}{\tid{waiting}}} = \bid{next\_stop}
	}{
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\\\reduces
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T[\bid{critical} \leftarrow T(\bid{critical})+1], W\setminus\{\tuple{\bid{src}, \bid{critical}, \tokenOf{\bid{critical} + 1}, \tid{waiting}}\}}}{\switches}{\signals}}
	}
\end{mathpar}
\todo{ajouter $\tuple{\bid{next\_stop, \sigred}}, \tuple{\bid{src}, \siggreen}$}
\todo{expliquer \nextWait{E}}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{IncrBefore}] {
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\incr{\bid{critical}}}{A^\prime}
		\\
		\neg\exists \bid{src}, \tid{waiting} \text{ s.t. } \tuple{\bid{src}, \bid{critical}, \tokenOf{\bid{critical}} + 1, \tid{waiting}} \in W
	}{
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\\\reduces
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T[\bid{critical} \leftarrow T(\bid{critical})+1], W}}{\switches}{\signals}}
	}
\end{mathpar}

Then, when the waiting train arrives, instead of stopping the train, the regulator can update the signal and let it continue until its next waiting point. This case is identified when the token already has the value the train expects\footnote{Notice that if the train misses its slot, e.g. if an incorrect program increases twice the token, the train will not continue, as another train, waiting for the twice-increased value, might be on the tracks.}.
\begin{mathpar}
	\inferrule*[left=\ruleDef{WaitAfter}] {
		\bufhead{B} = \tuple{\tid{waiting}, \bid{id}}
		\and
		\tokenOf{\bid{critical}} = n
		\\
		\nextWait{\handlerOf{E}{\tid{waiting}}} = \bid{next\_stop}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\wait{\bid{critical}}{n}}{A^\prime}
	}{
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\reduces
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T, W}}{\switches}{\signals}}
	}
\end{mathpar}
\todo{M-à-J des feux}

\begin{mathpar}
	\inferrule*[left=\ruleDef{Auth}] {
		\bufhead{E[\tid{id}]}.pos = \bid{id}
		\and
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\\
		\nextWait{\buftail{E[\tid{id}]}} = \bid{wait}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\auth}{A^\prime}
	}{
			\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
			\reduces
			\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T, W}}{\switches}{\signals}}
	}
\end{mathpar}\todo{ajouter $\tuple{\bid{wait}, \sigred}, \tuple{\bid{id}, \siggreen}$ dans le buffer des signaux}
where \nextWait{E} returns the next position (block id) where the train has to was, using the event handlers of the train in question. Notice that, in our case, we consider the tail of the event handlers of the train, since it is already waiting and we want the next waiting location. \todo{rephrase}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{EndEvent}]{
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \emptyList
	}{
		\redTuple{\guardR}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\reduces
		\redTuple{\guardS}{\buftail{B}}{\stateTuple{\trainSeq}{\tuple{\popHandlerHead{E}{\tid{id}}, T, W}}{\switches}{\signals}}
	}
\end{mathpar}

@@

Given a system state  $S = \redTuple{x}{B}{\stateTuple{\trainSeq{}}{\regulator}{\switches}{\signals}}$ and a train $\tid{id}$, 
\begin{itemize}
	\item   we say that it has no jobs if  $\trainSeq{}[\tid{id}].P = \emptyTrainProg$;
	\item its source is $\mathtt{src}(S, \tid{id}) = \trainSeq{}[\tid{id}].pid$;
	\item its destination is $\mathtt{dst}(S, \tid{id}) = pid \in \blocks $ if either
	\begin{itemize}
		\item  it has no jobs and  $\trainSeq{}[\tid{id}].pid = pid$  or
		\item  the last order in  $\trainSeq{}[\tid{id}].P$ is $\su{d}{pid}$ for some direction $d$.
	\end{itemize}
\end{itemize}

A system state $S = \redTuple{\guardT}{\emptyset}{\stateTuple{\trainSeq{}}{\regulator}{\switches}{\signals}} $  is \emph{reliable} if: 
\begin{itemize}
	\item  no two trains meet on the same block or the same switch, \todo{En dire plus}
	\item $S$ has  a unique normal form $S'$ and 
	\item any train in $S'$ has no jobs and 
	\item for any train $\tid{id}$, $\mathtt{dst}(S, \tid{id}) =  \mathtt{dst}(S', \tid{id})$. 
\end{itemize}

@@

Two states $S$ and $S'$ are said to be \emph{compatible} whenever:
\begin{itemize}
\item for any train $\tid{id}$, we have $\mathtt{dst}(S, \tid{id})  =  \mathtt{src}(S', \tid{id})$,
\item for any normal form $S \reduces^! S''$, we have $S''.\sigma = S'.\sigma$.
\end{itemize}
In other words, at the arrival of $S$, trains are at the starting position of $S'$ and so are switches. We define the composition on compatible states. Actually, we describe composition of a system state and a safe step. So, from the remaining of the section, we suppose $S$ and $S'$ be compatible state, $S'$ being a safe step. We aim to compute their composition $S''  = \redTuple{x}{B}{\stateTuple{\trainSeq}{\regulator}{\switches}{\signals}}$.

>>>>

%% Buffer
\newcommand{\bufferFmt}[1]{#1}
\newcommand{\head}[1]{\ensuremath{{\tt hd}(#1)}}
\newcommand{\buflen}[1]{\ensuremath{{\tt len}(\bufferFmt{#1})}}
\newcommand{\bufhead}[1]{\head{\bufferFmt{#1}}}
\newcommand{\buftail}[1]{\ensuremath{{\tt tl}(\bufferFmt{#1})}}
\newcommand{\emptyList}{\ensuremath{\varepsilon}}
\newcommand{\bufTrainSet}{\ensuremath{\bufferFmt{\mathbb{B}_t}}\xspace}
\newcommand{\bufSigSet}{\ensuremath{\bufferFmt{\mathbb{B}_s}}\xspace}
\newcommand{\bufTrain}{\ensuremath{\bufferFmt{B_t}}\xspace}
\newcommand{\bufSig}{\ensuremath{\bufferFmt{B_s}}\xspace}

%% Reduction relation
\newcommand{\reduces}{\ensuremath{\rightarrow}}
\newcommand{\redTuple}[4]{\ensuremath{\tuple{#1, \bufferFmt{#2}, \bufferFmt{#3}, #4}}}

@@

Train events are not dealt with instantly by the regulator (e.g. two train events can happen before the regulator begins to react to the first one). To characterise this behaviour, train events are stored in a buffer until the regulator uses them. In our model, a train event represent a train going from one block to another. When such thing happens, the train sends a message with its identifier to the regulator. A \emph{train buffer} \bufTrain is a sequence of such events, i.e. of train identifiers.
Similarly, the regulator communicates with signals with a \emph{signal buffer} \bufSig, which is a list of tuples $\tuple{\bid{id}, c}$, indicating that both signals of block $\bid{id}$ should be turned to color $c$. Let \bufTrainSet (resp. \bufSigSet) denote the set of train (resp. signal) buffers.

@@

States of the system are triples from $\{\guardR, \guardS, \guardT\} \times \bufTrainSet \times \bufSigSet \times \modelSet$. Our reduction relation is a binary relation on system states, noted $\reduces$: $S_1 \reduces S_2$ means that state $S_1$ can change to $S_2$ (note that this relation is not a function: $S_1$ can reduce to multiple states, due to non-determinism). We define $\reduces$ as the least relation induced by the inference rules presented hereafter.

@@

\todo{Enlever les bid dans le buffer des trains}
\begin{mathpar}
	\inferrule*[left=\ruleDef{Start}]{
		\dirFmt{d} \neq \dirFmt{d^\prime} \and P = \trainConcat{\su{d^\prime}{\posFmt{N}}}{P^\prime}
	}{
		\hspace{3mm} \redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{P}\}}{\regulator}{\switches}{\signals}} \\
		\reduces
		\redTuple{\guardT}{\push{\bufTrain}{\tuple{\tid{id}, \bid{id}}}}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d^\prime}{P}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}

Conversely, if the train program is empty (i.e. upon termination), the train stops using rule \ruleRef{Stop}.
\begin{mathpar}
	\inferrule*[left=\ruleDef{Stop}]{
		\dirFmt{d} \neq \dirStop
	}{
	\hspace{4mm}  \redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\emptyTrainProg}\}}{\regulator}{\switches}{\signals}} \\
	\reduces
	\redTuple{\guardT}{\push{\bufTrain}{\tuple{\tid{id}, \bid{id}}}}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{\dirStop}{\emptyTrainProg}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{Until}] {
		\suc{\bid{id}}{d}{\switches} = \bid{id^\prime} \neq \nosuc
		\and
		\signalF{\bid{id}}{d} = \siggreen
		\and
		\posFmt{N}\neq \varepsilon
	}{
		\redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\trainConcat{\su{d}{[\bid{id^\prime}; \posFmt{N}]}}{P}}\}}{\regulator}{\switches}{\signals}} \\
		\reduces		
		\redTuple{\guardS}{\push{\bufTrain}{\tuple{\tid{id}, \bid{id^\prime}}}}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id^\prime}}{d}{\trainConcat{\su{d}{[\posFmt{N}]}}{P}}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}

\begin{mathpar}
	\inferrule*[left=\ruleDef{UntilNext}] {
		\suc{\bid{id}}{d}{\switches} = \bid{id^\prime} \neq \nosuc
		\and
		\signalF{\bid{id}}{d} = \siggreen
	}{
		\redTuple{\guardT}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id}}{d}{\trainConcat{\su{d}{[\bid{id^\prime}]}}{P}}\}}{\regulator}{\switches}{\signals}} \\
		\reduces		
		\redTuple{\guardS}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}\cup\{\trainTuple{\tid{id}}{\bid{id^\prime}}{d}{P}\}}{\regulator}{\switches}{\signals}}
	}
\end{mathpar}
Notice that, in \ruleRef{UntilNext}, no message is added to the buffer.
\todo{@Lucas, expliquer pourquoi c'est pas nécessaire.}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{StartEvent}] {
		\buflen{B} \neq 0
	}{
		\redTuple{\guardT}{\bufTrain}{\bufSig}{R} \reduces \redTuple{\guardR}{\bufTrain}{\bufSig}{R}
	}
\end{mathpar}

@@

Rule \ruleRef{Turn} triggers when a \turn{\sid{id}}{s} is encountered in the event handler. It updates the state of the targeted switch.
\begin{mathpar}
	\inferrule*[left=\ruleDef{Turn}]{
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\turn{\sid{id}}{s}}{A^\prime}
	}{
	\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
	\reduces
	\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T, W}}{\updateSignals{\switches}{\sid{id}}{s}}{\signals}}
	}
\end{mathpar}

@@

To execute a \wait{\bid{critical}}{n} order, the regulator stores the train id in its waiting set, together with the current block of the train (\bid{src}), the block it is waiting for (\bid{critical}), and the value the token associated with the target block has to reach to release the train ($n$).
\begin{mathpar}
	\inferrule*[left=\ruleDef{WaitBefore}] {
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\wait{\bid{critical}}{n}}{A^\prime}
		\\
		\tokenOf{\bid{critical}} \neq n
	}{
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\\\reduces
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T, W\cup\tuple{\bid{src}, \bid{critical}, n, \tid{id}}}}{\switches}{\signals}}
	}
\end{mathpar}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{IncrAfter}] {
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\incr{\bid{critical}}}{A^\prime}
		\\
		\exists \bid{src}, \tid{waiting} \text{ s.t. } \tuple{\bid{src}, \bid{critical}, \tokenOf{\bid{critical}} + 1, \tid{waiting}} \in W
		\\
		\nextWait{\handlerOf{E}{\tid{waiting}}} = \bid{next\_stop}
	}{
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\\\reduces
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T[\bid{critical} \leftarrow T(\bid{critical})+1], W\setminus\{\tuple{\bid{src}, \bid{critical}, \tokenOf{\bid{critical} + 1}, \tid{waiting}}\}}}{\switches}{\signals}}
	}
\end{mathpar}
\todo{ajouter $\tuple{\bid{next\_stop, \sigred}}, \tuple{\bid{src}, \siggreen}$}
\todo{expliquer \nextWait{E}}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{IncrBefore}] {
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\incr{\bid{critical}}}{A^\prime}
		\\
		\neg\exists \bid{src}, \tid{waiting} \text{ s.t. } \tuple{\bid{src}, \bid{critical}, \tokenOf{\bid{critical}} + 1, \tid{waiting}} \in W
	}{
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\\\reduces
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T[\bid{critical} \leftarrow T(\bid{critical})+1], W}}{\switches}{\signals}}
	}
\end{mathpar}

Then, when the waiting train arrives, instead of stopping the train, the regulator can update the signal and let it continue until its next waiting point. This case is identified when the token already has the value the train expects\footnote{Notice that if the train misses its slot, e.g. if an incorrect program increases twice the token, the train will not continue, as another train, waiting for the twice-increased value, might be on the tracks.}.
\begin{mathpar}
	\inferrule*[left=\ruleDef{WaitAfter}] {
		\bufhead{B} = \tuple{\tid{waiting}, \bid{id}}
		\and
		\tokenOf{\bid{critical}} = n
		\\
		\nextWait{\handlerOf{E}{\tid{waiting}}} = \bid{next\_stop}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\wait{\bid{critical}}{n}}{A^\prime}
	}{
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\reduces
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T, W}}{\switches}{\signals}}
	}
\end{mathpar}
\todo{M-à-J des feux}

\begin{mathpar}
	\inferrule*[left=\ruleDef{Auth}] {
		\bufhead{E[\tid{id}]}.pos = \bid{id}
		\and
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\\
		\nextWait{\buftail{E[\tid{id}]}} = \bid{wait}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \regConcat{\auth}{A^\prime}
	}{
			\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
			\reduces
			\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{\substHandlerHead{E}{\tid{id}}{A^\prime}, T, W}}{\switches}{\signals}}
	}
\end{mathpar}\todo{ajouter $\tuple{\bid{wait}, \sigred}, \tuple{\bid{id}, \siggreen}$ dans le buffer des signaux}
where \nextWait{E} returns the next position (block id) where the train has to was, using the event handlers of the train in question. Notice that, in our case, we consider the tail of the event handlers of the train, since it is already waiting and we want the next waiting location. \todo{rephrase}

@@

\begin{mathpar}
	\inferrule*[left=\ruleDef{EndEvent}]{
		\bufhead{B} = \tuple{\tid{id}, \bid{id}}
		\and
		\head{\handlerOf{E}{\tid{id}}} = \emptyList
	}{
		\redTuple{\guardR}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\tuple{E, T, W}}{\switches}{\signals}}
		\reduces
		\redTuple{\guardS}{\buftail{\bufTrain}}{\bufSig}{\stateTuple{\trainSeq}{\tuple{\popHandlerHead{E}{\tid{id}}, T, W}}{\switches}{\signals}}
	}
\end{mathpar}

@@

Given a system state  $S = \redTuple{x}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq{}}{\regulator}{\switches}{\signals}}$ and a train $\tid{id}$, 
\begin{itemize}
	\item   we say that it has no jobs if  $\trainSeq{}[\tid{id}].P = \emptyTrainProg$;
	\item its source is $\mathtt{src}(S, \tid{id}) = \trainSeq{}[\tid{id}].pid$;
	\item its destination is $\mathtt{dst}(S, \tid{id}) = pid \in \blocks $ if either
	\begin{itemize}
		\item  it has no jobs and  $\trainSeq{}[\tid{id}].pid = pid$  or
		\item  the last order in  $\trainSeq{}[\tid{id}].P$ is $\su{d}{pid}$ for some direction $d$.
	\end{itemize}
\end{itemize}

A system state $S = \redTuple{\guardT}{\emptyset}{\bufSig}{\stateTuple{\trainSeq{}}{\regulator}{\switches}{\signals}} $  is \emph{reliable} if: 
\begin{itemize}
	\item  no two trains meet on the same block or the same switch, \todo{En dire plus}
	\item $S$ has  a unique normal form $S'$ and 
	\item any train in $S'$ has no jobs and 
	\item for any train $\tid{id}$, $\mathtt{dst}(S, \tid{id}) =  \mathtt{dst}(S', \tid{id})$. 
\end{itemize}

@@

Two states $S$ and $S'$ are said to be \emph{compatible} whenever:
\begin{itemize}
\item for any train $\tid{id}$, we have $\mathtt{dst}(S, \tid{id})  =  \mathtt{src}(S', \tid{id})$,
\item for any normal form $S \reduces^! S''$, we have $S''.\sigma = S'.\sigma$.
\end{itemize}
In other words, at the arrival of $S$, trains are at the starting position of $S'$ and so are switches. We define the composition on compatible states. Actually, we describe composition of a system state and a safe step. So, from the remaining of the section, we suppose $S$ and $S'$ be compatible state, $S'$ being a safe step. We aim to compute their composition $S''  = \redTuple{x}{\bufTrain}{\bufSig}{\stateTuple{\trainSeq}{\regulator}{\switches}{\signals}}$.
